%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\input{glyphtounicode}
\pdfgentounicode=1

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.25in,top=0.6in,right=0.25in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref} % For urls
\usepackage{marvosym} % For Phone icon (Mobilefone), Email icon (Email)
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Daniel Connelly} % Your name
\address{Portland, Oregon} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{\Mobilefone 503-504-4930  \Email \href{mailto:connellyd2050@gmail.com}{connellyd2050@gmail.com} \\ \href{https://github.com/danc2050}{GitHub: Danc2050} \\ \href{https://www.linkedin.com/in/dconnelly2/}{LinkedIn: dconnelly2}} % Your phone number and email
\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Portland State University} 
  \\{\bf {\em Master of Science in Computer Science}}, { G.P.A: 3.74 }\hfill {\em January 2019 - March 2020}
  \\{ \small{ \hspace{10mm} - Graduate Courses:}} {\small{Cybersecurity, Blockchain Development \& Security, Artificial Intelligence, Machine Learning, Operating Systems, Data Structures \& Algorithms, Programming Languages}}
  \\ {\bf \em Grad-prep Computer Science}, { G.P.A: 3.6 }\hfill {\em January 2018 - January 2019}
  \\ {\bf \em Bachelor of Science in Psychology}, { G.P.A: 3.82 }\hfill {\em October 2017 - January 2018}  
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

\begin{rSection}{Objective}
  I am interested in Software Development, Software Engineering, or anything that touches the software lifecycle really. Courses and projects have taught me varying disciplines that have equipped me to be a good Software Engineer. Namely, graduate courses in Networks, Operating Systems, Programming Languages, Blockchain, and others. I enjoy unique problems and solving them with varying languages such as Java, C, C++, and Python.
\end{rSection}
%--------------------------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Projects}
  {\bf \href{https://docs.google.com/presentation/d/11ACdzalpubDKvJFnA6a\_5ST7Dd3P\_EbLrq1DEpJKloM/edit#slide=id.p}{Capstone Sponsor}} \hfill {\em{Spring 2020 - Present}}
  \\• Applicant sponsor for an Agile team of 5-6 students to work on an automated bug submission software.\\
    \\{\bf \href{https://www.haveibeenexploited.com/}{Digital Registry of Vulnerable Ethereum Programs}} \hfill {\em{June 2019 - Present}}
  \\• Employed exhaustive Symbolic Execution over $\approx1.7$ million programs, finding $\approx800,000$ of them to contain security vulnerabilities.
  \\• Utilized Python for scripting and programming, Docker for isolation of containers, Linux for its easy infrastructure, and Git for version control.
  \\• Co-built a React app and Go server to intake HTTP and MySQL database requests. Setup and managed DNS configuration and SSL certification of a public facing website which was deployed to Google App Engine and later hosted on a Google Compute Engine instance.\\
  \\{\bf \href{https://github.com/tdulcet/Send-Msg-CLI/tree/python-port}{Email and Text Notification}} \hfill {\em{March 2020 - Present}}
  \\• Porting a Bash script to Python which is capable of sending emails, texts, attachments, alerts when a program finished, and digitally signing emails.
  \\• Increased feature set by approximately 5 (config option, multiple operating system compatibility...).\\
  \\{\bf Password Cracking} \hfill {\em{April 2019}}
  \\• Cracked 60 salted passwords by using the C library SHA1 hash of a dictionary of words with salts.
  \\• Experimented with other hashing techniques and encryption algorithms (e.g., RSA, HMAC, MD5).

\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}
  {\bf{Programming Languages}} C, C++, Java, Python, Solidity, JavaScript\\
  {\bf{Operating Systems}} Linux, Windows, Mac\\
  {\bf{Other Skills}} Git, Google Cloud Platform (GCP), Amazon Web Services (AWS), SQL, MySQL, PostgreSQL, Docker, Trello, Travis CI, Continuous Integration (CI), Continuous Deployment (CD), 

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

  \begin{rSubsection}{Portland State University}{{\em{September 2019 - March 2020}}}{Graduate Research Assistant}{}
\item • $\$10,000$ in total grants: $\$5,000$ Google Cloud Grant, $\$5,000$ Portland State University Grant.
  \\• Research and present a thesis on the current state of security for Ethereum Smart Contracts.
  \\• Secure software development included the use of C/C++ in running API calls to gather data.
\end{rSubsection}

  \begin{rSubsection}{Portland State University}{{\em{September 2019 - January 2020}}}{Computer Science Tutor}{}
\item • Tutor 10-15 lower-division students per week in object-oriented programming, discrete structures, and x86 assembly to improve academic performance.
\\• Help students in debugging, troubleshooting, and designing assignments in C, C++, and Java.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	CERTIFICATIONS 
%----------------------------------------------------------------------------------------

\begin{rSection}{Certifications, Awards, Publications, Volunteering}

{\bf{SoloLearn Programming Language Certifications:}} 
  \href{https://www.sololearn.com/Certificate/1089-17953779/pdf/?mode=download}{C}, 
  \href{https://www.sololearn.com/Certificate/1051-17953779/pdf/?mode=download}{C++},
  \href{https://www.sololearn.com/Certificate/1068-17953779/pdf/?mode=download}{Java},
  \href{https://www.sololearn.com/Certificate/1073-17953779/pdf/?mode=download}{Python}, 
  \href{https://www.sololearn.com/Certificate/1060-17953779/pdf/?mode=download}{SQL} \hfill {\em{March 31 2020}}\\
{\bf{Google Cloud Research Grant:}} \$5,000 \hfill {\em{September 2019}}\\
  {\bf{Portland State University/NSF Grant:}} \href{https://www.nsf.gov/awardsearch/showAward?AWD\_ID=1821841}{\$5,000} \hfill {\em{September 2019}}\\
  {\bf{MS Thesis:}} \href{https://www.slideshare.net/DanielConnelly15/daniel-connelly-ethereum-smart-contract-masters-thesis}{\itshape{Smart Contract Vulnerabilities on the Ethereum Blockchain: A Current Perspective \hfill {\em{May 11 2020}}}}\\
  {\bf{Women in Computer Science (WiCs):}} Member/Mentor \hfill {\em{September 2019 - March 2020}}\\
  {\bf{Association of Computer Machinery (ACM):}} Treasurer \hfill {\em{December 2018 - 2019}}\\
  {\bf{BS Thesis:}} \href{https://pdxscholar.library.pdx.edu/honorstheses/496/}{\itshape{Delays in Treatment: A Literature Review of Pathways to Treatment for Psychosis \hfill{\em{January 1 2018}}}}\\
  {\bf{Honors College Graduate (BS):}} Magna Cum Laude \hfill {\em{January 2018}}\\

\end{rSection}






\iffalse
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Academic Achievements} 
 Runners up in B.G.Shirke Vidyarthi Competition for Innovative Project organized by Pune Construction Engineering Research Foundation in January 2018
\item Won First Prize in Model Making Competition Organized by Symbiosis Institute of Technology, Pune.
\end{rSection}

\newpage

%----------------------------------------------------------------------------------------
% Extra Curricular
%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Cirrucular} \itemsep -3pt
\item Co-Organized “ Nirmitee 2017” - a National Symposium of Civil Department of MIT, Pune
\item Attended a workshop on Autodesk Revit at IIT Bombay in 2014.
\item Winner of Inter Departmental Football Competition 2015.
\item Member of the  Rotaract Club Of Pune Pride from 2014 to 2017.
\item Worked for a start-up company Named OUST as a Regional Marketing Manager
%\item Trained and disciplined in National Cadet Corps (NCC), IIT Kanpur for a year.
 %\item  Participated in Vijyoshi Camp 2012 organized at Indian Institute of Science, Bangalore.
 %\item Won 2nd position in Kho-Kho in Intramurals conducted by Physical Education Section, IIT Kanpur.
 %\item Pursued French as second language during secondary school from Grade 6 to Grade 10. Also participated in French Song Competition and French G.K. Quiz in Class 10th. %

\end{rSection}

\begin{rSection}{Personal Traits}
\item Highly motivated and eager to learn new things.
\item Strong motivational and leadership skills.
\item Ability to work as an individual as well as in group.
\end{rSection}
\fi
\end{document}
